CommonMind Consortium: DLPFC

### 2020-10-12 combined_analysis/CTS/GABA.Rmd
consistant names
drop genes that don't vary

---
title: "CommonMind Consortium: DLPFC"
subtitle: "Cell type specific analysis of read count data by cohort"
author:
- name: "[Gabriel Hoffman](http://gabrielhoffman.github.io)$^{1}$ and Kelsey Montgomery$^{2}$"
  affiliation: | 
    [1] Icahn School of Medicine at Mount Sinai, New York
    [2] Sage Bionetworks, Seattle, WA
date: "Run on `r Sys.time()`"
documentclass: article
output:
  html_document:
    toc: true
    toc_float: true
params:
  upload: FALSE
  cellType: "GABA"
---

@@

thisFileName <- 'GABA'

@@

  new("EList", list(E = geneExpr[,idx], weights = 1/geneExpr.se[rownames(geneExpr), colnames(geneExpr)][,idx]))
  })
names(vobj.lst) = levels(METADATA$Cohort)
```

@@

```{r store, eval=TRUE}
if( params$upload ){    
  # Code
  # Make sure these match the folder name and parent Id in the first chunk.
  CODE <- Folder(name = activityName, parentId = parentId)
  CODE <- synStore(CODE)

@@

  # Standard analysis
  # storeData( "geneCountsMerged", "Merged DLPFC counts for both cohorts")
  storeData( "METADATA", "Merged metadata used here for both cohorts")
  storeData( "isexpr", "Genes used in this analysis")
  storeData( "vobj.lst", "Voom results for each cohort")
  storeData( "resid.add", "Residuals correcting for covariates and add back - (Dx_Sex Dx Sex)")
  storeData( "fit_marginal.lst", "dream fit for marginal analysis")
  storeData( "res_zenith", "zenith results from fit_marginal.lst")
  storeData( "res_meta_zenith", "Meta-analysis of zenith results from fit_marginal.lst")
  storeData( "res_meta_zenith.sex_autosome", "Meta-analysis of zenith results from fit_marginal.lst - just autosomal genes")
  storeData( "df_DE_results", "Differential expressed genes within each cohort")
  storeData( "df_meta", "Meta-analysis of differential expression across cohorts")

>>>>

---
title: "CommonMind Consortium: DLPFC"
subtitle: "Cell type specific analysis of read count data by cohort"
author:
- name: "[Gabriel Hoffman](http://gabrielhoffman.github.io)$^{1}$ and Kelsey Montgomery$^{2}$"
  affiliation: | 
    [1] Icahn School of Medicine at Mount Sinai, New York
    [2] Sage Bionetworks, Seattle, WA
date: "Run on `r Sys.time()`"
documentclass: article
output:
  html_document:
    toc: true
    toc_float: true
params:
  upload: TRUE
  cellType: "GABA"
---

@@

thisFileName <- 'GABA.Rmd'

@@

  # get variance withing cohort
  # only keep genes with variance > 0
  v = apply( geneExpr[,idx], 1, var)

  E = geneExpr[v > 0,idx]

  new("EList", list(E = E, weights = 1/geneExpr.se[rownames(E), colnames(E)]))
  })
names(vobj.lst) = levels(METADATA$Cohort)
```

@@

```{r store, eval=TRUE}

if( params$upload ){    
  # Code
  # Make sure these match the folder name and parent Id in the first chunk.
  CODE <- Folder(name = gsub(":", " -",activityName), parentId = parentId)
  CODE <- synStore(CODE)

@@

  # Standard analysis
  # storeData( "geneCountsMerged", "Merged DLPFC counts for both cohorts")
  storeData( "METADATA", "Merged metadata used here for both cohorts")
  # storeData( "isexpr", "Genes used in this analysis")
  storeData( "vobj.lst", "Voom results for each cohort")
  storeData( "resid.add", "Residuals correcting for covariates and add back - (Dx_Sex Dx Sex)")
  storeData( "fit_marginal.lst", "dream fit for marginal analysis")
  storeData( "res_zenith", "zenith results from fit_marginal.lst")
  storeData( "res_meta_zenith", "Meta-analysis of zenith results from fit_marginal.lst")
  storeData( "res_meta_zenith.sex_autosome", "Meta-analysis of zenith results from fit_marginal.lst - just autosomal genes")
  storeData( "df_DE_results", "Differential expressed genes within each cohort")
  storeData( "df_meta", "Meta-analysis of differential expression across cohorts")

### 2020-10-12 combined_analysis/CTS/Glu.Rmd
drop genes that don't vary

---
title: "CommonMind Consortium: DLPFC"
subtitle: "Cell type specific analysis of read count data by cohort"
author:
- name: "[Gabriel Hoffman](http://gabrielhoffman.github.io)$^{1}$ and Kelsey Montgomery$^{2}$"
  affiliation: | 
    [1] Icahn School of Medicine at Mount Sinai, New York
    [2] Sage Bionetworks, Seattle, WA
date: "Run on `r Sys.time()`"
documentclass: article
output:
  html_document:
    toc: true
    toc_float: true
params:
  upload: FALSE
  cellType: "Glu"
---

@@

```{r store, eval=TRUE}
if( params$upload ){    
  # Code
  # Make sure these match the folder name and parent Id in the first chunk.
  CODE <- Folder(name = activityName, parentId = parentId)
  CODE <- synStore(CODE)

>>>>

---
title: "CommonMind Consortium: DLPFC"
subtitle: "Cell type specific analysis of read count data by cohort"
author:
- name: "[Gabriel Hoffman](http://gabrielhoffman.github.io)$^{1}$ and Kelsey Montgomery$^{2}$"
  affiliation: | 
    [1] Icahn School of Medicine at Mount Sinai, New York
    [2] Sage Bionetworks, Seattle, WA
date: "Run on `r Sys.time()`"
documentclass: article
output:
  html_document:
    toc: true
    toc_float: true
params:
  upload: TRUE
  cellType: "GLU"
---

@@

```{r store, eval=TRUE}
if( params$upload ){    
  # Code
  # Make sure these match the folder name and parent Id in the first chunk.
  CODE <- Folder(name = gsub(":", " -",activityName), parentId = parentId)
  CODE <- synStore(CODE)

### 2020-10-12 combined_analysis/CTS/MgAs.Rmd
drop genes that don't vary

@@

    # Compute residuals which adding back Diagnosis and Sex effects
    resid.lst = fitVarPartModel(vobj, form_use, info, fxn = f, BPPARAM = SnowParam(18))  
    do.call(rbind, resid.lst)
    })
  names(residuals.lst) = names(vobj.lst)

>>>>

v = apply(geneExpr, 1, var)

@@

    # Compute residuals which adding back Diagnosis and Sex effects
    resid.lst = fitVarPartModel(vobj, form_use, info, fxn = f, BPPARAM = SnowParam(4))  
    do.call(rbind, resid.lst)
    })
  names(residuals.lst) = names(vobj.lst)
